A simple R markdown example

### 2019-11-11 R/rmarkdown.Rmd
sync image and source of markdown example close #59

---
title: "An Example"
author: "Aaron Peikert & Andreas Brandmaier"
date: "9/3/2019"
output: pdf_document
papersize: "a6"
geometry:
  - "landscape"
  - margin=0.5cm
header-includes:
   - \usepackage[center,dvips,frame]{crop}
---

@@

The data was never before anylized in this way. Except in `help(t.test)`.

@@

I can now assert that what I *believe* to be true
--- that there is a difference in mean between the groups ---
is `r ifelse(result$p.value > .025, "**not**", "")` supported by data.

>>>>

---
title: "A simple R markdown example"
author: "Aaron Peikert & Andreas M. Brandmaier"
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: pdf_document
papersize: "a6"
geometry:
  - "landscape"
  - margin=0.5cm
header-includes:
   - \usepackage[center,dvips,frame]{crop}
---

@@

This is an example of students' sleep data taken from `help(t.test)`.

@@

I can now assert that what I *believe* to be true
--- that there is a difference in means between the groups ---
is `r ifelse(result$p.value > .025, "**not**", "")` the supported by the data.
